Initial estuarine response to the nutrient dense Piney Point wastewater discharge into Tampa Bay, Florida

### 2021-10-13 manu-draft.Rmd
precip to redtide figure, update figure caption

```{r redtide, fig.cap = '*Karenia brevis* concentrations (100k cells/L) and number of fish kill reports for the contiguous record showing cell concentrations (a) by year and (b) by week in 2021 and reported fish kills by city (Tampa, St. Petersburg) (c) by year and (d) by week in 2021. Red tide concentrations show minimum, 25th percentile, median, 75th percentile, and maximum for each year or week for middle and lower Tampa Bay. *K. brevis* cell counts are from NOAA Harmful Algal BloomS Observing System (HABSOS, https://www.ncei.noaa.gov/maps/habsos), Fish kill reports are from Florida Fish and Wildlife Conservation Commission, Fish and Wildlife Research Insitute Fish Kill Database, attributed to *K. brevis* (https://public.myfwc.com/FWRI/FishKillReport/).'}
knitr::include_graphics('figs/redtide.jpeg')
```

>>>>

```{r redtide, fig.cap = '*Karenia brevis* concentrations (100k cells/L) (a) by year and (b) by week in 2021, (c) fish kill reports in 2021, (d) cumulative precipitation in 2021 compared to past years, and (e) wind rose plots for 2021 before, passage (two days pre/post), and after tropical storm Elsa. Red tide concentrations show minimum, 25th percentile, median, 75th percentile, and maximum for each year or week for middle Tampa Bay. *K. brevis* cell counts are from NOAA Harmful Algal BloomS Observing System (HABSOS, https://www.ncei.noaa.gov/maps/habsos), Fish kill reports are from Florida Fish and Wildlife Conservation Commission, Fish and Wildlife Research Insitute Fish Kill Database, attributed to *K. brevis* (https://public.myfwc.com/FWRI/FishKillReport/), precipitation data are from Tampa International Airport, and wind rose plots are from St. Petersburg, Florida.  Wind roses show relative counts of six minute observations in directional (30 degree bins) and speed (m/s) categories.'}
knitr::include_graphics('figs/redtide.jpeg')
```
